combined

### 2021-08-31 analysis/combined.Rmd
nbn

library(modelbased)
estimate_contrasts(model1, test = "bf")
```
```{r}
#https://easystats.github.io/blog/posts/bayestestr_emmeans/
inswath_main <- pairs(emmeans(model1, ~ trt))

@@

```{r}
library(ggrepel)
em %>% as_tibble() %>% 
  mutate(sprayer = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
  mutate(emmean = round(emmean, 1)) %>% 
  ggplot(aes(x = fct_reorder(trt, emmean), y = emmean,
             color = trt, shape = sprayer, label = emmean)) +
  geom_point(size = 3) +
  geom_jitter(data = inswath %>% 
                rename(emmean = deposition), alpha = 0.1) +
  scale_color_viridis_d(option = "H") +
  coord_flip() +
  geom_text_repel(  size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 455) +
  scale_shape_manual(values = c(16, 1)) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD), size = 1.2) +
  ylim(0, 2000) +
  theme_few() +
  labs(x = NULL, 
       y = expression(paste("Spray particle deposition (\u03B7L/cm"^"2",")"))
       ) +
  theme(legend.position = "none",
        axis.title = element_text(size = 30),
        axis.text = element_markdown(size = 25)) -> figA

@@

```{r include=TRUE}
fig2 %>% 
  mutate(trt = str_replace(trt, "Intact", "DRA")) %>% 
  mutate(hood = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
  ggplot(aes(x = distance_m, y = predicted, color = trt, 
             fill = trt, label = formula, shape = hood)) +
  scale_color_viridis_d(option = "H") + 
  scale_fill_viridis_d(option = "H") + 
  geom_line(fill = NA) +
  geom_point(alpha = 0.5) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), 
              alpha = 0.3, color = NA) +
  facet_wrap(~ trt, ncol = 3) +
  scale_shape_manual(values = c(16, 1)) + 
  theme_few() +
  geom_text(data = loc, mapping = aes(x = 10, y = 20), 
            label = "Intercept", inherit.aes = FALSE, size = 10) +
  geom_text(data = loc, mapping = aes(x = 55, y = 10), 
            label = "Slope", inherit.aes = FALSE, size = 10) +
  geom_label(aes(label = formula), x = 30, y = 15, color = "white", size = 12) +
  geom_curve(data = loc, mapping = aes(x = 25, y = 17,
             xend = 20, yend = 20),
             arrow = arrow(length = unit(0.07, "inch")), 
             color = 1,
             size = 0.4, curvature = 0.3, inherit.aes = FALSE) +
  geom_curve(data = loc, mapping = aes(x = 42, y = 13,
             xend = 47, yend = 10),
             arrow = arrow(length = unit(0.07, "inch")), 
             color = 1,
             size = 0.4, curvature = 0.3, inherit.aes = FALSE) +
  labs(x = "Distance (m)", 
       y = expression(paste("Spray particle deposition (\u03b7L/cm"^"2",")"))) +
  theme(legend.position = "none",
        legend.text = element_markdown(size = 20),
        legend.background = element_blank(),
        axis.title = element_markdown(size = 32),
        axis.text = element_markdown(size = 28),
        strip.background = element_blank(),
        strip.text = element_textbox(
          size = 32,
          face = "bold",
          color = "white", 
          fill = "#494949", 
          box.color = "#282728",
          halign = 0.5, linetype = 1, r = unit(5, "pt"), width = unit(1, "npc"),
          padding = margin(2, 0, 1, 0), 
          margin = margin(3, 3, 3, 3)))

@@

```{r}
epred3$emmeans %>% as_tibble() %>% 
  mutate(sprayer = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
  mutate(emmean = round(emmean, 1)) %>% 
  ggplot(aes(x = fct_reorder(trt, emmean), y = emmean,
             color = trt, shape = sprayer, label = emmean)) +
  geom_point(size = 3) +
  geom_jitter(data = auc_data %>% 
                rename(emmean = auc), alpha = 0.02) +
  scale_color_viridis_d(option = "H") +
  geom_text_repel(
                    size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 545) +
  coord_flip() +
  scale_shape_manual(values = c(16, 1)) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD), size = 1.2) +
  scale_y_continuous(breaks = c(0, 50, 100, 150, 200, 250)) +
  theme_few() +
  labs(x = NULL, y = "Area under the curve") +
  theme(legend.position = "none",
        legend.text = element_markdown(size = 20),
        legend.background = element_blank(),
        axis.title = element_markdown(size = 30),
        axis.text = element_markdown(size = 25)) -> figE
figE
```
```{r}
#https://easystats.github.io/blog/posts/bayestestr_emmeans/
auc_main <- pairs(emmeans(auc_model, ~ trt))

@@

```{r}
c + figE +
  plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 35, hjust = 0, vjust = 0)) -> figU

ggsave("Figure 3.png", width = 8, height = 4)
```

>>>>

library(modelbased)
estimate_contrasts(model1, test = "bf")
```

```{r}
#https://easystats.github.io/blog/posts/bayestestr_emmeans/
inswath_main <- pairs(emmeans(model1, ~ trt))

@@

```{r}
library(ggrepel)
em %>% as_tibble() %>% 
  mutate(sprayer = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
  mutate(emmean = round(emmean, 1)) %>% 
  ggplot(aes(x = fct_reorder(trt, emmean), y = emmean,
             color = trt, shape = sprayer, label = emmean)) +
  geom_point(size = 3) +
  geom_jitter(data = inswath %>% 
                rename(emmean = deposition), alpha = 0.1) +
  scale_color_viridis_d(option = "H") +
  coord_flip() +
  geom_text_repel(  size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 455) +
  scale_shape_manual(values = c(16, 1)) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD), size = 1.2) +
  ylim(0, 2000) +
  theme_few() +
  labs(x = NULL, 
       y = expression(paste("In-swath spray deposition  (\u03B7L/cm"^"2",")"))
       ) +
  theme(legend.position = "none",
        axis.title = element_text(size = 30),
        axis.text = element_markdown(size = 25)) -> figA

@@

```{r include=TRUE}
fig2 %>% 
  mutate(trt = str_replace(trt, "Intact", "DRA")) %>% 
  mutate(hood = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
  ggplot(aes(x = distance_m, y = predicted, color = trt, 
             fill = trt, label = formula, shape = hood)) +
  scale_color_viridis_d(option = "H") + 
  scale_fill_viridis_d(option = "H") + 
  geom_line(fill = NA) +
  geom_point(alpha = 0.5) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), 
              alpha = 0.3, color = NA) +
  facet_wrap(~ trt, ncol = 3) +
  scale_shape_manual(values = c(16, 1)) + 
  theme_few() +
#  geom_text(data = loc, mapping = aes(x = 10, y = 20), 
#            label = "Intercept", inherit.aes = FALSE, size = 10) +
#  geom_text(data = loc, mapping = aes(x = 55, y = 10), 
##            label = "Slope", inherit.aes = FALSE, size = 10) +
  geom_label(aes(label = formula), x = 30, y = 15, color = "white", size = 12) +
#  geom_curve(data = loc, mapping = aes(x = 25, y = 17,
#             xend = 20, yend = 20),
#             arrow = arrow(length = unit(0.07, "inch")), 
#             color = 1,
#             size = 0.4, curvature = 0.3, inherit.aes = FALSE) +
#  geom_curve(data = loc, mapping = aes(x = 42, y = 13,
#             xend = 47, yend = 10),
#             arrow = arrow(length = unit(0.07, "inch")), 
#             color = 1,
#             size = 0.4, curvature = 0.3, inherit.aes = FALSE) +
  labs(x = "Distance (m)", 
       y = expression(paste("Spray particle deposition (\u03b7L/cm"^"2",")"))) +
  theme(legend.position = "none",
        legend.text = element_markdown(size = 20),
        legend.background = element_blank(),
        axis.title = element_markdown(size = 32),
        axis.text = element_markdown(size = 28),
        strip.background = element_blank(),
        strip.text = element_textbox(
          size = 32,
          face = "bold",
          color = "white", 
          fill = "#494949", 
          box.color = "#282728",
          halign = 0.5, linetype = 1, r = unit(5, "pt"), width = unit(1, "npc"),
          padding = margin(2, 0, 1, 0), 
          margin = margin(3, 3, 3, 3)))

@@

```{r}
epred3$emmeans %>% as_tibble() %>% 
  mutate(sprayer = if_else(str_detect(trt, "Open"), "Open", "Hood")) %>% 
  mutate(emmean = round(emmean, 1)) %>% 
  ggplot(aes(x = fct_reorder(trt, emmean), y = emmean,
             color = trt, shape = sprayer, label = emmean)) +
  geom_point(size = 3) +
  geom_jitter(data = auc_data %>% 
                rename(emmean = auc), alpha = 0.02) +
  scale_color_viridis_d(option = "H") +
  geom_text_repel(
                    size = 8,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 545) +
  coord_flip() +
  scale_shape_manual(values = c(16, 1)) +
  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD), size = 1.2) +
  scale_y_continuous(breaks = c(0, 50, 100, 150, 200, 250)) +
  theme_few() +
  labs(x = NULL, y = "Area under the curve") +
  theme(legend.position = "none",
        legend.text = element_markdown(size = 20),
        legend.background = element_blank(),
        axis.title = element_markdown(size = 30),
        axis.text = element_markdown(size = 25)) -> figE
#figE

ggsave("Figure 3.png", width = 5, height = 4)
```

```{r}
#https://easystats.github.io/blog/posts/bayestestr_emmeans/
auc_main <- pairs(emmeans(auc_model, ~ trt))

@@

```{r}
#c + figE +
#  plot_annotation(tag_levels = 'A') & 
#  theme(plot.tag = element_text(size = 35, hjust = 0, vjust = 0)) -> figU

#ggsave("Figure 3.png", width = 8, height = 4)
```
